\subsection{What is IPFS? What does it offer?}

Many of the terms used below are explained in detail in the Background
section.

IPFS is a distributed file system.  The word file here is used with a
wide meaning -- e.g., it can be a ledger record.  Currently (2018),
only an alpha version is implemented.  It can be installed from
\url{ipfs.io} into a Linux, Windows, or Mac system.

IPFS whitepaper by Juan Benet
\url{https://medium.com/@ConsenSys/an-introduction-to-ipfs-9bba4860abd0}

youtube.comNovember 19, 2016
The Decentralized Web, IPFS and Filecoin - Juan Benet
Recorded at the Silicon Valley Ethereum Meetup - October 22nd, 2016

youtube.com December 8, 2016 The next Internet Revolution | Juan Benet
| TEDxSanFrancisco Juan explains why the web is in danger and how
there's an open source movement focused on creating a new way of
sharing knowledge is building the Interplanetary Files System
(IPFS).The Interplanetary Files System (IPFS), an open source movement
focused on creating a new way of sharing knowledge.

IPFS is a distributed file system that seeks to connect all computing
devices with the same system of files.  In some ways, this is similar
to the original aims of the Web, but IPFS is actually more similar to
a single bittorrent swarm exchanging git objects. IPFS could become a
new major subsystem of the internet. If built right, it could
complement or replace HTTP. It could complement or replace even
more. It sounds crazy. It is crazy.”[1]

``IPFS is a global, versioned, peer-to-peer filesystem. It combines
good ideas from Git, BitTorrent, Kademlia, SFS, and the web. It is
like a single bittorrent swarm, exchanging git objects. IPFS provides
an interface as simple as the HTTP web, but with permanence built
in. You can also mount the world at /ipfs.IPFS could become a new
major subsystem of the internet. If built right, it could complement
or replace HTTP.''
\url{https://alternativeto.net/software/ipfs/}

``IPFS is a new hypermedia distribution protocol, addressed by content and identities. IPFS enables the creation of completely distributed applications. It aims to make the web faster, safer, and more open.''
New? 201x?

``Ten terrible attempts to make the Inter Planetary File System human-friendly
This article is part 6 of the Blockchain train journal, start reading
here: Catching the Blockchain Train.
hackernoon.comSeptember 26, 2017''

decentralized.blog August 10, 2017
Understanding the IPFS White Paper part 1
This article is part 4 of the Blockchain train journal, start reading
here: Catching the Blockchain Train. The crypto currency/blockchain
world loves its white papers, and IPFS is no exception.

https://blockchainmind.com/ipfs/

https://blockonomi.com/interplanetary-file-system/

``Most people aren't running IPFS nodes, and IPFS isn't seen yet as a
valuable resource by censors. So they'll probably just block the whole
domain, and now people won't know about or download IPFS. We saw this
progression with GitHub in China.''

