\documentclass[12pt]{article}
\def\fat{\framebox[1mm]{\rule{0mm}{2mm}}}
\def\pr{$\parallel$}
\def\rar{$\rightarrow$}
\def\CSP{{\sc csp}}
\def\RPC{{\sc rpc}}
\def\SR{{\sc sr}}

\parindent=0pt
\begin{document}


{\bf CEG 
{\large \bf 730 Distributed Computing Principles}\\[5pt]
Final Exam\quad Nov 29, 1999\quad 100 points max \quad 120 minutes}\\
{Mateti,  Fall Quarter 1999, Wright State U}\\[-5pt]
\bigskip
\hrule

\begin{enumerate}

\item (8*5 points)
Explain, in a few lines, the truth or falsity of the following
statements.

\begin{enumerate}

\item
Any solution to the {\em distributed mutual exclusion} problem can be
thought of as a solution to the problem of implementing semaphores in
a distributed system, and vice versa.

\item
A {\em critical assertion} is one without which a program will abort.

\item A ``safety'' property is defined thus: Let {\sc bad} be a
{predicate} characterizing a ``bad'' {state} of program code segment
S.  Assume that {\{P\} S \{Q\}} holds.  Assume that I is a {global
invariant}.  If I $\Rightarrow$ $\neg$ {\sc bad}, we say that $\neg$
{\sc bad} is a safety property for S.  Thus, it all depends on whether
{\em we} consider a certain property good or bad.

\item
``Some day, if not at the end of {\sc ceg} 730, you will appreciate
and marvel at the book {\em Concurrent Programming} by Andrews.''
Explain if this is a safety, or liveness property, or perhaps neither.

\item
Asynchronous message passing cannot be implemented using synchronous
message passing primitives.

\item
The \CSP\ code {\tt [X!2 \pr Y!3]} is equivalent to \\
{\tt
[  true \rar\ X!2; Y!3 \fat\ true \rar\ Y!3; X!2]}

\item
In \SR, when invoking an operation implemented by a {\tt proc} through
a {\tt send} the effect is that of a rendezvous.

\item
Java RMI is RPC applied in the context of the Java language.

\end{enumerate}

\item (25 points)
Given: A bag $B$ of integers, and the size $b$ of it.  It is known
that each element in the bag appears exactly $d$ times.  We wish to
delete the duplicates resulting in a set of only $b/d$ distinct
elements that occurred in the bag.  It is guaranteed that $d > 0, b >
0$.  Unfortunately, the value $d$ is unavailable and needs to be
computed by examining the bag $B$.

Design (15 points, with full explanation) and implement (10 points) a
solution in C-Linda.  Assume that the tuple space already contains
{\tt <"B", i>} for all {\tt i} in $B$, and the size of the bag {\tt
<"nB", b>}.  You lose 2 points for {\sl each} use of {\tt inp} or {\tt
rdp}.  As usual, we wish to maximize concurrency, we prefer a
symmetric solution, and correctness rates much much higher than
efficiency.

\item (25 points)
We discussed in class the {\em Mine Sweeper} game of Windows.  Each
cell contains a small collection (say less than 5) of processes.  Program these
in \CSP\ so that  all the cells together behave as the game does.
Explain your solution fully.


\item (10 points) The following is claimed to be an implementation of
{\bf region $v$ when $B$ do $S$ end}.  Either give a convincing
argument that the above algorithm is correct, or give a scenario
demonstrating a situation that violates a requirement of the problem.
Nothing is given regarding the semaphores if they are weak, strong,
etc.

{\bf
\begin{tabbing}
00\=00\=00\=\kill
semaphore $e := 1$, $g := 0$, $d := 0$ initially;\\
integer $nd := 0$, $ng := 0$ initially;\\
\\
P$(e)$;\\
while not $B$ do\+\\
  $nd := nd + 1$;\\
  if $ng > 0$ then V$(g)$ else V$(e)$ fi;\\
  P$(d)$;\\
  P$(g)$;\\
  $ng := ng - 1$\-\\
od;\\
$S$;\\
while $nd > 0$ do\+\\
  V$(d)$;\\
  $nd := nd - 1$;\\
  $ng := ng + 1$\-\\
od;\\
if $ng > 0$ then V$(g)$ else V$(e)$ fi
\end{tabbing}
}


\end{enumerate}
\end{document}
