\documentstyle[12pt]{article}
\def\fat{\framebox[1mm]{\rule{0mm}{2mm}}}
\def\CSP{{\sc csp}}
\def\RPC{{\sc rpc}}
\parindent=0pt
\begin{document}


{\bf CEG 
\large \bf 730 Distributed Computing Principles\\[5pt]
\large Mid Term Exam\\[10pt]
Oct 22, 1992 \quad 100 points max \quad 75 minutes\\
}
\bigskip
{Mateti,  Fall Quarter 1992, Wright State U}\\[-5pt]
\hrule

\begin{enumerate}

\item (5*5 points)
Explain, in a few lines, the truth or falsity of the following
statements.

\begin{enumerate}
\item
Every distributed system must also be a concurrent system.

\item
There is no difference between safety and liveness properties.

\item
The difference between asynchronous and synchronous message
passing is trivial.

\item
We need only have one clock per node in order to correctly compute a
happened-before relation.

\item Marshalling in \RPC\ is no more than a tight-packing
of the bytes of the input arguments or resulting values.

\end{enumerate}

\item (30 points)
We have a \CSP\ process {\tt C} that outputs an unending stream of
non-negative numbers to a process named, say, {\tt X}.  We want {\tt
X} to be able to receive requests of the form {\tt X!nthmin(n)} from a
user process {\tt U} and respond with {\tt U!x}, where $x$ is the
$n$-th smallest number it has seen so far from {\tt C}.  If {\tt X}
has seen fewer than $n$ numbers so far, or if $n$ is greater than 10,
or less than 1, the value of $x$ to use is -1.  Write the process {\tt
X} in \CSP.  Maximize concurrency.  Process {\tt C} must not suffer
delays.

\item (20 points)
Describe a token-passing distributed termination algorithm.  Do not
assume that the process graph is a tree.


\item (10+15 points)  Udding's solution to the mutual exclusion problem
is reproduced below.  (a) Explain the purpose of each of the
semaphores, using invariants. (b) In the Concluding remarks section,
the author comments ``In this program as in previous programs that
implement semaphores, the order of two V-operations, viz., {\tt V(eu)}
and {\tt V(qu)}, turns out to be crucial.''  There are three
occurrences of {\tt V(eu)}.  Which one is he referring to?  Explain
what would happen if we exchange {\tt V(eu)} with {\tt V(qu)}.

\begin{verbatim}
 1 P(eu); ne := ne+1; V(eu);
 2 P(qu); P(eu);	    
 3	nm := nm+1;	    
 4	ne := ne-1;	    
 5	if ne > 0 --> V(eu) 
 6	[] ne = 0 --> V(mu) 
 7	fi;		    
 8 V(qu);		    
 9 P(mu); nm := nm-1;	    
10	<cs >		    
11	if nm > 0 -->  V(mu)
12	[] nm = 0 -->  V(eu)
13	fi		    
\end{verbatim}

\end{enumerate}
\end{document}
