\documentstyle[12pt]{article}
\def\fat{\framebox[1mm]{\rule{0mm}{2mm}}}
\def\CSP{{\sc csp}}
\def\RPC{{\sc rpc}}
\def\SR{{\sc sr}}
\def\co{{\bf co}}
\def\oc{{\bf oc}}
\def\pa{{$\parallel$}}
\def\lb{\langle}
\def\rb{\rangle}
\def\ra{$\rightarrow$}
\def\await{{\bf await}}
\textheight=8.1in
\parindent=0pt
\begin{document}


{\bf CEG 
\large \bf 730 Distributed Computing Principles\\[5pt]
\large Final Exam\\[10pt]
June 10, 1993 \quad 100 points max \quad 120 minutes\\
}
\bigskip
{Mateti,  Spring Quarter 1993, Wright State U}\\[-5pt]
\hrule

\begin{enumerate}

\item (5*5 points)
Explain, in a few lines, the (degree of) truth or falsity of the
following statements.

\begin{enumerate}
\item
The little-endian-ness of a machine has no relevance to \RPC.

\item
{\sl All} client-server applications are based on \RPC.


\item
\RPC\ cannot be used for peer-to-peer distributed computing.


\item
The \CSP\ code {\tt [X!2 \pa\ Y!3]} is equivalent to \\
{\tt
[  true \ra\ X!2; Y!3\\
\fat\ true \ra\ Y!3; X!2\\
]}

\item
The ``standard'' solution \quad {\tt P(m); CS; V(m);} \noindent is not
starvation-free only in the distributed systems context, but is
ok when the system is a single-cpu system.


\end{enumerate}

\item (4*15 points)
The stable marriage problem is the following.  There are $n$ ``men,''
and the same number of ``women.''  Each woman ranks the men from $1$ to
$n$, and each man ranks the women from $1$ to $n$.  A pairing is a
one-to-one correspondence of men and women.  A pairing is stable if,
for two women $w_1$ and $w_2$ and their paired men $m_1$ and $m_2$,
both the following conditions are satisfied:

1. $w_1$ ranks $m_1$ higher than $m_2$, or $m_2$ ranks $w_2$ higher than $w_1$; and\\
2. $w_2$ ranks $m_2$ higher than $m_1$, or $m_1$ ranks $w_1$ higher than $w_2$.

Put slightly differently, a pairing is unstable if a woman and man
would both prefer each other to their current pairing.  A solution to
the stable marriage problem is a set of $n$ pairings, all of which are
stable.

\begin{enumerate}
\item Give a predicate that specifies the goal.

\item Write a \CSP\ algorithm that solves the problem.  Each person
becomes a process.  In addition, you can have a few additional
processes; the more additional processes you have the more points you
lose.  Assume that the rankings are already availbale in an array
local to each man/woman process.  Explain your solution strategy.

\item Write an \SR\ program that solves the problem.  Each person
becomes a process within a resource.  In addition, you can have a few
additional processes; the more additional processes you have the more
points you lose.  Assume that the rankings are already availbale in an
array local to each man/woman process.  Explain your solution
strategy.

\item Write a C-Linda algorithm that solves the problem.  Assume that
the number $n$, and the rankings are already availbale in the tuple
space: $\lb ``w'', i, j, r \rb$ is the rank $r$ given by woman $i$ to
man $j$; similarly $\lb ``m'', i, j, r \rb$.  Explain your solution
strategy.  The number of processes is a constant $c$.

\end{enumerate}


\item (15 points)
Study the following code as a `solution' for the starvation-free
mutual exclusion problem.  Make the same assumption regarding weak
semaphores that [Morris 79] and [Udding 86] do.

\begin{verbatim}
local x, y;  global z=0, b=false, s[0]=1, s[1]=1;
x := z;
P(s[x]);
  if z = x then
    y := 1 - z;
    P(s[y]);
      z := y;
      repeat
        b := true;
        V(s[x]);
        P(s[x]);
      until b;
      <critical section>
    V(s[y])
  else
    b := false;
    <critical section>
  fi
V(s[x])
\end{verbatim}
Either give a convincing argument that the above algorithm is correct,
or give a scenario demonstrating a situation that violates the
requirements of the problem.

\end{enumerate}
\end{document}
