\documentclass[12pt]{article}
\def\fat{\framebox[1mm]{\rule{0mm}{2mm}}}
\def\ellipsis{\ldots}
\def\pbar{\parallel}
\def\rar{\rightarrow}
\def\CSP{{\sc csp}}
\def\RPC{{\sc rpc}}
\def\co{{\bf co}}
\def\oc{{\bf oc}}
\def\pa{{$\parallel$}}
\def\lb{$\langle$}
\def\rb{$\rangle$}
\def\ra{$\rightarrow$}
\def\await{{\bf await}}
\def\zand{\wedge}\def\zor{\vee}	\def\znot{\neg}
%\topmargin 0pt
\parindent=0pt
\begin{document}


{\bf CEG 
\large \bf 730 Distributed Computing Principles}\\[5pt]
{Mateti,  Spring Quarter 2000, Wright State U}\\
{\bf Final Exam}\quad June 6, 2000 \quad 100 points max \quad 120 minutes\\
\hrule

\begin{enumerate}

\item (8*5 points)
Explain, in a few lines, the truth or falsity of the statements.

\begin{enumerate}

\item Suggest a mechanism similar to RPC but in the context of Linda.

\item ``Some day, if not at the end of {\sc ceg} 730, you will
appreciate the book {\em Concurrent Programming} by Andrews.''
Explain if this is a safety, or liveness property, or perhaps neither.

\item In the Andrews' distributed semaphore implementation of our
textbook that we discussed, there are numerous {\sc ack} messages
being sent.  They can be reduced in number by O(n).

\item All the following are correct:

(i) wp( S, True ) = True  for any aribtrary S,\\
(ii) wp(S, True ) = False defines liveness,\\
(iii) wp(S, False) = False is impossible,\\
(iv) wp(S, False)  = True means S will not terminate,\\
(v) wp(S, True) = undefined is unexpected because of  safety.

\item In the following (alleged) solution for the Readers/Writers
problem with priority for writers, the semaphore m3 and the P(m3) and
V(m3) operations are needed only if the number of writers far exceeds
that of readers.

\begin{minipage}[t]{2.5in}
\begin{verbatim}
P(m3);
 P(r);
  P(m1);
    nr++;
    if nr == 1 then P(w) fi;
  V(m1);
 V(r);
V(m3);
...read...
P(m1);
 nr --;
 if nr == 0 then V(w) fi;
V(m1)
\end{verbatim}
\end{minipage}\vline\quad
\begin{minipage}[t]{2in}
\begin{verbatim}
P(m2);
 nw ++;
 if nw == 1 then P(r) fi;
V(m2);
P(w);
...write...
V(w);
P(m2);
 nw--
 if nw == 0 then V(r) fi;
V(m2)
\end{verbatim}
\end{minipage}

\item The famous Dining Philosophers Problem illustrates livelocks
among other properties.

\item Process A and B have the following requirements.  If A enters a
certain ``room", before it can leave the room it must wait until it
``meets" B, and vice versa.  This cannot be solved using semaphores.

\item Consider the precondition and statement \{$x \ge 4$\} \lb x
:= x - 4\rb.\quad This interferes with (a) \{$x \ge 10$\} \lb x
:= x + 5\rb \{ $x \ge 11 $\} but not with (b) \{ $x$ is odd \}
\lb y := x + 1 \rb \{ $y$ is even \}.


\end{enumerate}

\item (20 points)
Describe a distributed termination algorithm, with or without tokens.
The process graph is a binary tree.


\item (20*2 points) In both items below $a_i$ is the same as {\tt
a[i]}.  Solve the problem in Linda and in CSP.  Just writing (psuedo-)
code is not enough.  You must explain and justify how/why your
algorithm works.  \\

(a) Assume that the Linda tuple space is loaded with tuples \lb
``nt'', $n_t$\rb, \lb ``nd'', $n_d$\rb, \lb ``d'', d\rb, \lb{}``p'', p
\rb so that $0 \le n_d \le n_t$, and \lb ``s'', i, $a_i$ \rb, for $1
\le i \le n_t$, so that the $a_i$ sequence is sorted in the
non-decreasing order.  In this sequence there are {\em at least} $n_d$
occurrences of $d$ which need to be removed.  Develop a C-Linda
solution for this removal and adjustment of indices $i$ for numbers
beyond the deleted $d$'s.  At the end, the tuple space contains the
$a_i$ after the removal of $d$'s.  Use $p$ processes.  Assume that $p
<< n_t$.

(b) The values $a_i$, for $1 \le i \le n_t$, are now held by CSP
processes $P_i$, one per process, as in the Small Set of Integers.
Initially, the $a_i$ sequence is sorted in the non-decreasing order.
$P_0$ sends $d$ to $P_1$, which sends it to $P_2$, etc.  Write a \CSP
algorithm so that all $d$ are ``removed''.  Note that no $n_d$ is
given.  At the end, the $a_i$ sequence should be sorted in the
non-decreasing order.

\end{enumerate}

\end{document}
