\section{ADPP App}\label{apkcreated}

We created an application named ANU DASHBOARD OF PAST AND PRESENT
PROCESS. This has 5 various tabs - Past Processes, Basic Info,
Application, Process and Net Stats.  The tabs

\begin{itemize}
\item Past process has process name, process id, time started,
  time ended, files opened, files written, files read, network
  connection it spawned.
\item Basic Info has details of internal storage, sd card storage, battery, memory, processor.
\item Application Info has details of all the running application, its
  package name, user id, install date, file size.
\item Process has details of running processes, process id, user id,
  state, importance, lru
\item Net stats - It displays the network details, local/remote
  address, state.
\end{itemize}

\subsection{Past Processes}

In the past process tab, the list of all the past processes name are
listed based in a chronoligaical order. We can select the time from
when the past processes should be listed - last one hour, last one day
and last one week.  When we click on each past process, we get the
details like pid, time started, time ended, files opened, files
written, network connection it used.

\subsection{Basic Info}
In the basic info tab details like battery, SD card storage, A2SD
storage, internal storage, system storage, system cache, processor and
memory are listed.  When we click on the battery item, we get details
like level, health, status, technology, voltage, temperature, plugged.
When we click on the processor, we get details like model, current
frequency, cpu frequency range and scaling governor.

\subsection{Application}	
Under the Application tab, all the current running applications are
listed.  When we click on each application, we get details like
package name, user id, file size, public source, install date,
permission, \TBD{cMags} and enabled.

\subsection{Processes}
Under the Processes tab, all the current processes are
displayed. Color differentiation is given for different type of
processes like - foreground process(blue), background process (yellow),
system services (grey).  When we click on each process, we get details
like process name, process id, user id, group id, state(sleeping,
runnin,.), threads, importance, lru, package name.

\subsection{Net Stats}
Under Net Stats, we get the details of the protocol used, local/remote
address, state of the protocol.  The current network type, local
address, roaming state, ip address are displayed.



   
