
\section{Distributed Apps}

https://karl.tech/simple-dapp-architecture/ 2016

DApp:: { medium.comAugust 13, 2017 The ultimate end-to-end tutorial to
  create and deploy a fully decentralized Dapp in ethereum In this
  tutorial my objective is to walk you through the steps required to
  create a descentralized application from start to finish and deploy
  it in ethereum.

news.ycombinator.comMarch 29, 2018
OpenBazaar 2.0, powered by IPFS : Hacker News
How do you intend to prevent sybil attacks on seller ratings? Since there are no account sign ups and subsequent verifications, it would be theoretically possible to create a large number of accounts with fake reviews. There are a few factors that still make reviews somewhat useful though.

hackernoon.comJune 11, 2018
A short trip to Jupyter via the Inter-planetary File System
IPFS is the Distributed Web. It is an idea and a protocol designed to
support a distributed file system that seeks to connect all computing
devices with the same system of files. There has been plenty of hype
around IPFS, but much of it is well-deserved.

nytimes.comJune 8, 2018
Beyond the Bitcoin Bubble
The sequence of words is meaningless: a random array strung together
by an algorithm let loose in an English dictionary. What makes them
valuable is that they’ve been generated exclusively for me, by a
software tool called MetaMask. In the lingo of cryptography, they’re
known as my seed phrase.

}

{
https://d.tube/
https://news.ycombinator.com/item?id=16481112
heimindanger Feb 2018

A good old website? No.
We don't need the domain, you can take the https://github.com/dtube/production repository, ipfs add -r it on ipfs, and use DTube this way -> https://ipfs.io/ipfs/QmRWPnY8h7Eg4v74GtKT6UBy2kUAN139QwYPUrg... (few bugs but it works apart from /home not being rendered on first load, you need to click the logo)

What is decentralised:

- The website (its fully static and can be hosted on ipfs)

- The video storage (IPFS)

- The account system / commenting / voting / subscribing (when you do that, it directly creates the transaction on the blockchain)

What isnt decentralised:

- The upload endpoints (upldr*.d.tube). You can legitimately avoid it if you have a local IPFS node running and you add files yourself, however it's really not convenient for users.

- The search endpoint (asksteem.com). This is used for the search, tags browsing, and related videos.

- Server side rendering stuff for robots only (we enabled that recently)

P.S: I am the founder of DTube
}

{
  BitKariero A decentralised record of professional credentials http://students.cs.ucl.ac.uk/2016/group15/index.html
\url{https://github.com/bitkariero}
students.cs.ucl.ac.uk

Architecture. The backbone of our application is built on Ethereum and
IPFS.
}


{Vlattice https://github.com/danielquinn/vlattice/ A "video lattice",
this will essentially be a federated YouTube, but realistically, it
could be used for permanent distribution of files of any type.
}

https://medium.com/@prinox2/credito-decentralizing-financial-intelligence-9e7ff231b38f

https://jazzteam.org/en/company-news/development-of-decentralized-applications/

https://maidsafe.net/ ``The World's First Autonomous Data Network''
DOWNLOAD SAFE BROWSER
Web Hosting Manager
Create and publish websites
SAFE Mail Tutorial
End to end encrypted desktop mail tutorial

Blockchain & Web3.0 Era needs Paradigm Shift in Web CMS
Architecture!!!  Medium ... architectural evolution journey that an
organization take to become ready to embrace upcoming decentralized
world spearheaded by IPFS and Blockchain.
https://medium.com/@PankajSinghV/blockchain-web3-0-era-needs-paradigm-shift-in-web-cms-architecture-c475ff93390b
Pankaj Verma Learning Life. Working as Architect at IBM | Indian
Institute of Technology, Delhi Mar 4

InterPlanetary File System (IPFS) Tutorial - Building the ...  YouTube
InterPlanetary File System (IPFS) Tutorial - Building the Distributed
Web https://www.youtube.com/watch?v=6kqgsGXpykM Learn more advanced
front-end and full-stack development at:
https://www.fullstackacademy.com The InterPlanetary File System (IPFS)
is a new internet protocol that aims to upgrade the web and replace
HTTP. In this IPFS tutorial, we discuss the reasons why we need a new
internet protocol and walk through how the IPFS creates a distributed,
peer-to-peer network with content-based addressing that makes the web
faster, more resilient, and permanent.  Watch this video to learn: -
The disadvantages of the current internet protocol - What the
InterPlanetary File System (IPFS) is and how it works - How the IPFS
can solve the problems the current internet protocol presents


A Distributed Cloud Robotics Middleware Architecture for Trust-minimized Storage and Computation
Alessandro Simovic, Ralf Kaestner, Martin RufliPublished 2017


Intro to
Decentralized Systems
Nicola Greco
Protocol Labs


https://tools.ietf.org/html/rfc6920 Naming Things with Hashes
April 2013

https://www.rfc-editor.org/info/rfc1035 Domain names - implementation
and specification, November 1987


https://www.w3.org/2016/04/blockchain-workshop/slides/benet-ipfs.pdf
juan benet
2016-06-29

https://medium.com/karachain/peer-to-peer-protocols-explained-3b1d947c4600
Go to the profile of Syed Jafar Naqvi Syed Jafar Naqvi Co-Founder/CEO
at Karachain Nov 21, 2017 Read this before building a Distributed
System What is a DHT Chord is one of the four original DHT protocols,
along with CAN, Tapestry and Pastry, and was developed at the MIT.

@phdthesis{greco2017decentralized,
  title={Decentralized infrastructure for file storage},
  author={Greco, Nicola and others},
  year={2017},
  school={Massachusetts Institute of Technology}
}

https://www.researchgate.net/profile/Antonio_Tenorio-Fornes/publication/325435917_Open_Peer-to-Peer_Systems_over_Blockchain_and_IPFS_an_Agent_Oriented_Framework/links/5b20c9590f7e9b0e373f0ae1/Open-Peer-to-Peer-Systems-over-Blockchain-and-IPFS-an-Agent-Oriented-Framework.pdf
