
\section{Background}\label{seBackground}

Juan Benet (the BDFL of IPFS).

https://decentralized.blog/catching-the-blockchain-train.html

\url{https://decentralized.blog/understanding-the-ipfs-white-paper-part-2.html}
figures.

\subsection{HTTP}
\subsection{BlockChain}
\subsection{Web Sockets}
\subsection{TBD}
\subsection{TBD}
\subsection{TBD}


\url{https://ipfs.io/docs/getting-started/} Add more details.

peer-to-peer systems
distributed file system

Kademlia + BitTorrent + Git
non-blockchain protocol
an object storage engine (think S3)
IPFS Companion 2.2.0 brings window.ipfs to your Browser ipfs.io

a dat version

File Permanance
decentralized 

Censor-Proof Networks


youtube.comFebruary 18, 2017
Juan Benet: Enter the Merkle Forest
Juan Benet, founder of IPFS and Filecoin, describes IPLD and "The Merkle Forest" at the IPFS Ethereum Hackathon hosted by MetaMask, Seattle 2017.

{Ethereum: A single shared computer living on the network, modeled
  after Bitcoin. It's essentially a computer everyone can trust to
  store data and to execute code.}

\subsection{Hashes}

\begin{verbatim}
$ echo -n 'hello' > /tmp/hello.txt
$ sha256sum /tmp/hello.txt
2cf24dba5fb0a30e26e83b2ac5b9e29e1b161e5c1fa7425e73043362938b9824  /tmp/hello.txt
\end{verbatim}

Double-sha256 is sha256(sha256(data)); note the missing ``sum''.

\subsection{MerkleTree}

A Merkle tree is an n-ary tree in which every leaf node is labelled
with the hash of a data block and every non-leaf node is labelled with
the hash of the labels of its child nodes.  Merkle trees are typically
implemented as binary trees,.

Figures/merkle-bin-tree.png
Figures/merkle-tree.jpg
Figures/merkle-tree-2.png

Once built, data can be audited (known as a Merkle-Proof) using only
the root hash in logarithmic time to the number of leaves.
\url{https://en.bitcoin.it/wiki/Protocol_documentation#Merkle_Trees}

\subsection{Blockchain}
